\documentclass[12pt]{article}
\usepackage[a4paper, total={170mm, 257mm}, top= 20mm]{geometry}
\usepackage{hyperref}
\usepackage{setspace, titlesec}

\titleformat{\section}[display]{\normalfont\small\bfseries}{}{0pt}{\Large}
\titlespacing*{\section}{0pt}{-15pt}{10pt}

\doublespacing\begin{document}
\title{Criterion A: Planning\vspace{-3em}}
\date{}
\author{}

\maketitle

\section{Description of the scenario}

My client, Mr.\ xx, has approached me with a game idea of his. He is fond of
the tile sliding game, where the aim is to complete a picture or some other
sequence by sliding a set
of tiles in a grid, but wished that he would be able to use his own pictures,
such as photos of his family or vacations. He was looking for a ``laid back
experience, something that is accessible to [him]''. He added that once he ``gets
stuck'', he would like to have an option to see hints, or have the computer
finish solving the puzzle. However, he also emphasized that he is quite
competitive, and would want a high score system and if possible, a way to
compete against others.

\section{Rationale for the solution}

The received description of the program required defined the approach needed for
this specific project. I chose the \href{https://godotengine.org/}{Godot game
engine} to implement the game in, due to my previous, although severly limited,
experience with it. Its scripting language, GDscript, closely resembles Python
and offers a rich object oriented approach to programming in a coherent package.
Additionally, exporting the final product as an executable for most platforms
(Windows, Mac, Linux, Android, iOS) is a streamlined process. Furthermore, the
engine was known historically for its 2D graphics capabilities, something that
would be required for the visual representation.

The final product would be restricted to the local device, due to the client
not being able to operate a server for it and also due to security concerns.
However, it will be made possible to utilize third-party cloud providers to
synchronize certain aspects between devices if Mr.\ xx chooses to.

\section{Success criteria}

\input{../success_criteria.tex}

\end{document}
